---
title: "Writing Reports with R Markdown"
output: html_document
date: "2023-03-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include = FALSE}
library(tidyverse)

```
```{r data, include = FALSE}
gapminder_1997 <- read_csv("data/gapminder_1997.csv")
```
This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy, and C02 emissions. Our goal is to determine......


```{r gdp_lifeexp_1997, echo=FALSE}

ggplot(data = gapminder_1997) + 
  aes(x= gdpPercap, y = lifeExp, color = continent, size = pop/1000000) +
  geom_point() + 
  labs(x = "GDP Per Capita" , y = "Life Expectancy", title = "Do people in wealthy countries live longer?", size = "Population (in millions)")

```

```{r varaibles, include = FALSE}
nCountries <- gapminder_1997 %>%
  select(country) %>%
  n_distinct()  #gives the number of distinct values in the column selected

minGDP <- gapminder_1997 %>%
  summarise(round(min(gdpPercap))) %>% 
  pull()

maxGDP <- gapminder_1997 %>%
  summarise(round(max(gdpPercap))) %>%
  pull()
```


The above plot shows the relationship between GDP per capita and life expectancy for a total of `r nCountries` countries. For this set of countries, economic wealth ranged from a minimum o USD `r minGDP` to a maximum of USD `r maxGDP`  per capita.



|Header 1 | Header 2 |
|---------|----------|
|row 1, column 1 |row 1, column 2|
|row 2, column 1 |row 2, column 2|


|Summary of Data|
|---------|----------|
|Number of Countries|`r nCountries`|
|Minimum GDP per capita |`r minGDP`|
|Maximum GDP per capita |`r maxGDP`|  

```{r kabletable}
library(knitr)

gapminder_1997 %>%
  filter(continent == "Oceania") %>%
  kable() 

```

# Header 1
## Header 2
### My third header



# Exercise: 

### My list:

  *  **R**   
  *  *summarise()* 
  *  ***I want to learn how to do RNAseq analysis and heatmap figures in R***

1. 
  - **R**   
  - *summarise()* 
  - ***I want to learn how to do RNAseq analysis and heatmap figures in R*** 

1. **R**  
2. *summarise*  
3. ***I want to learn how to do RNAseq analysis and heatmap figures in R*** 
4. <https://www.markdownguide.org/> 


1. **R**  
1. *summarise*  
1. ***I want to learn how to do RNAseq analysis and heatmap figures in R*** 
1. [https://www.markdownguide.org/] (Great Markdown Guide) 




